On the adhesivity of EGGS

### 2025-02-24 calco/main.tex
minima

\emph{Synopsis}
The paper has the following structure. 
In Section~\ref{sec:ade} we briefly recall 
the theory of
\emph{$\mathcal{M}$-adhesive categories}
and of \emph{kernel pairs}.
In Section~\ref{sec:hyper} we present the graphical structures of our interest, 
namely (labelled) hypergraphs and term graphs, and we provide a
functorial characterisation, which allows for proving their adhesivity properties.
This is further expended in Section~\ref{hypereq} for describing hypergraphs 
and term graphs with equivalence and in Section~\ref{eggs} for capturing
their variants where the equivalences are closed with respect to operator application,
thus subsuming EGGs.
%
All the proofs have been moved to the appendix. For the sake of completeness, 
and in order to fix the notation, we prove all the results 
recalled in the background section, besides those that are original 
to our work.

>>>>

\emph{Synopsis}
The paper has the following structure. 
In Section~\ref{sec:ade} we briefly recall 
the theory of
\emph{$\mathcal{M}$-adhesive categories}
and of \emph{kernel pairs}.
In Section~\ref{sec:hyper} we present the graphical structures of our interest, 
 (labelled, acyclic) hypergraphs and term graphs, and we provide a
functorial characterisation, which allows for proving their adhesivity properties.
This is expended in Section~\ref{hypereq} for describing hypergraphs 
and term graphs with equivalence and in Section~\ref{eggs} for capturing
their variants where the equivalences are closed with respect to operator application,
thus subsuming EGGs.
%
All the proofs have been moved to the appendices. 
%For the sake of completeness, 
%and in order to fix the notation, we prove all the results 
%recalled in the background section, besides those that are original 
%to our work.
